### 2023-02-26 manuscript.tex
Merge pull request #298 from SORTEE-Github-Hackathon/phpb_luna_supp_mat [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/afbbe55b2ad8febebb104fc9358170f15b3a4596.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/afbbe55b2ad8febebb104fc9358170f15b3a4596/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4276518486

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/d42ec283f2696204f3fcc8bdcd6835260a492415/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/d42ec283f2696204f3fcc8bdcd6835260a492415}{SORTEE-Github-Hackathon/manuscript@d42ec28}
on February 20, 2023.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-s91uGRZ2}{}}%
\emph{About code owners}. (n.d.). GitHub Docs. Retrieved February 20, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}

\leavevmode\vadjust pre{\hypertarget{ref-1Co6ZZjF1}{}}%
\emph{About large files on GitHub}. (n.d.). GitHub Docs. Retrieved February 20, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}

\leavevmode\vadjust pre{\hypertarget{ref-RhBKe0MG}{}}%
\emph{About Projects}. (n.d.). GitHub Docs. Retrieved February 20, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}

\leavevmode\vadjust pre{\hypertarget{ref-TOsASkn5}{}}%
\emph{Adding a license to a repository}. (n.d.). GitHub Docs. Retrieved February 20, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}

@@

\leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved February 20, 2023, from \url{https://stat545.com/}

\leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved February 20, 2023, from \url{https://help.osf.io/article/211-connect-github-to-a-project}

\leavevmode\vadjust pre{\hypertarget{ref-T03Api6e}{}}%
\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved February 20, 2023, from \url{https://circleci.com/}

@@

\leavevmode\vadjust pre{\hypertarget{ref-NUXbp429}{}}%
\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved February 20, 2023, from \url{https://github.com/features/actions}

@@

\leavevmode\vadjust pre{\hypertarget{ref-1CM2EcdVk}{}}%
\emph{Git - A Short History of Git}. (n.d.). Retrieved February 20, 2023, from \url{https://git-scm.com/book/en/v2/Getting-Started-A-Short-History-of-Git}

@@

\leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved February 20, 2023, from \url{https://happygitwithr.com/}

@@

\leavevmode\vadjust pre{\hypertarget{ref-3UAritXO}{}}%
\emph{Issues · fmsabatini/sPlotOpen\_Manuscript}. (n.d.). GitHub. Retrieved February 20, 2023, from \url{https://github.com/fmsabatini/sPlotOpen_Manuscript}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Re6Eg2va}{}}%
\emph{Manubot - Manuscripts, open and automated}. (n.d.). Retrieved February 20, 2023, from \url{https://manubot.org}

@@

\leavevmode\vadjust pre{\hypertarget{ref-oGbKxHzj}{}}%
\emph{Using Git and GitHub}. (n.d.). Retrieved February 20, 2023, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/afbbe55b2ad8febebb104fc9358170f15b3a4596/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/afbbe55b2ad8febebb104fc9358170f15b3a4596}{SORTEE-Github-Hackathon/manuscript@afbbe55}
on February 26, 2023.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-s91uGRZ2}{}}%
\emph{About code owners}. (n.d.). GitHub Docs. Retrieved February 26, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}

\leavevmode\vadjust pre{\hypertarget{ref-1Co6ZZjF1}{}}%
\emph{About large files on GitHub}. (n.d.). GitHub Docs. Retrieved February 26, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}

\leavevmode\vadjust pre{\hypertarget{ref-RhBKe0MG}{}}%
\emph{About Projects}. (n.d.). GitHub Docs. Retrieved February 26, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}

\leavevmode\vadjust pre{\hypertarget{ref-TOsASkn5}{}}%
\emph{Adding a license to a repository}. (n.d.). GitHub Docs. Retrieved February 26, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}

@@

\leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved February 26, 2023, from \url{https://stat545.com/}

\leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved February 26, 2023, from \url{https://help.osf.io/article/211-connect-github-to-a-project}

\leavevmode\vadjust pre{\hypertarget{ref-T03Api6e}{}}%
\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved February 26, 2023, from \url{https://circleci.com/}

@@

\leavevmode\vadjust pre{\hypertarget{ref-NUXbp429}{}}%
\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved February 26, 2023, from \url{https://github.com/features/actions}

@@

\leavevmode\vadjust pre{\hypertarget{ref-1CM2EcdVk}{}}%
\emph{Git - A Short History of Git}. (n.d.). Retrieved February 26, 2023, from \url{https://git-scm.com/book/en/v2/Getting-Started-A-Short-History-of-Git}

@@

\leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved February 26, 2023, from \url{https://happygitwithr.com/}

@@

\leavevmode\vadjust pre{\hypertarget{ref-3UAritXO}{}}%
\emph{Issues · fmsabatini/sPlotOpen\_Manuscript}. (n.d.). GitHub. Retrieved February 26, 2023, from \url{https://github.com/fmsabatini/sPlotOpen_Manuscript}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Re6Eg2va}{}}%
\emph{Manubot - Manuscripts, open and automated}. (n.d.). Retrieved February 26, 2023, from \url{https://manubot.org}

@@

\leavevmode\vadjust pre{\hypertarget{ref-oGbKxHzj}{}}%
\emph{Using Git and GitHub}. (n.d.). Retrieved February 26, 2023, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}
